Expectations, Outcomes, and Challenges \\ of Modern Code Review

### 2013-01-06 sections/challenges.tex
put emphasis instead of quotes for categories

Our third research question seeks to understand the main challenges faced by the reviewers when performing modern code reviews, also with respect to the expected outcomes. We also seek to uncover the reason behind the mismatch between expectations and actual outcomes on finding defects in code reviews.

@@

Do understanding needs change with the expected outcome of code review? We included a question in the programmers’ survey to know how much understanding they needed to achieve each of the motivations listed in \figref{XXX3}. The outcome of the question is summarized in \figref{XXX5}. The respondents could answer with a four values Likert's scale, by selecting the understanding of the change they felt was required to achieve the specific outcome. The most difficult task from the understanding perspective is ``finding defects,'' immediately followed by ``alternative solutions.'' Both clearly stand out from the other items. The gap in understanding needs between ``finding defects'' and ``code improvement'' seems to corroborate our hypothesis that the difference in the number of comments about these two items in review comments is mostly due to understanding issues. Thus, if managers and developers want code review to match their need for ``finding defects,'' context and change understanding must be improved.

@@

By observing developers performing code reviews, we noticed that some started code reviews by thoroughly reading the accompanying textual description, while others went directly to a specific changed file. In the first group, the time required for putting the first review comments and understanding the change rationale was noticeably longer, and some of the comments were asking to clarify the reasons for a change. To better comprehend this situation, we included in our interview guideline a question about how the interviewees start code reviews. Participants explained that when they own or are very familiar with the files being changed, they have a better context and it is easier for them to understand the change submitted: \quotation{when doing code review I start with things I am familiar with, so it is easier to see what is going on.} When they are file owners, they often do not even need to read the description, but they \quotation{go directly to the files they own.} On the contrary, when they do not own files, or have to review new files, they need more information and try to get it from the description, which is deemed good when it states \quotation{what was changed and why.}

@@

Most of the respondents (798, 91\%) answered positively to the first question, motivating it with the fact that it takes time to familiarize with the code and \quotation{learn enough about the files being modified to understand their purpose, invariants, APIs, etc.,} because \quotation{big-picture impact analysis requires contextual understanding. When reviewing a small, unfamiliar change, it is often necessary to read through much more code than that being reviewed.} The comment of a developer anticipates the answer to the second question: \quotation{It takes a lot longer to understand unknown code, but even then understanding isn't very deep. With code I am familiar with I have more to say. I know what to say faster. What I have to say is deeper. And I can be more insistent on it.} In fact, the answer to the second question is positive in 716~(82\%) cases. The main difference with file owner comments is that they are substantially deeper, more detailed and insightful. A respondent explained: \quotation{Comments reflect their deeper understanding -- more likely to find subtle defects, feedback is more conceptual (better ideas, approaches) instead of superficial (naming, mechanical style, etc.)} another tried to boldly summarize the concept: \quotation{Difference between algorithmic analysis and comments on coding style. The difference is big.}
In fact, when the context is clear and understanding is very high, as in the case when the reviewer is the owner of changed files, code review authors receive comments that explore \quotation{deeper details,} are \quotation{more directed} and \quotation{more actionable and pertinent,} and find \quotation{more subtle issues.}

>>>>

Our third research question seeks to understand the main challenges faced by reviewers when performing modern code reviews, also with respect to the expected outcomes. We also seek to uncover the reasons behind the mismatch between expectations and actual outcomes on finding defects in reviews.

@@

Do understanding needs change with the expected outcome of code review? We included a question in the programmers' survey to know how much understanding they needed to achieve each of the motivations listed in \figref{XXX3}. The outcome of the question is summarized in \figref{XXX5}. The respondents could answer with a four values Likert's scale, by selecting the understanding of the change they felt was required to achieve the specific outcome. The most difficult task from the understanding perspective is \emph{finding defects}, immediately followed by \emph{alternative solutions}. Both clearly stand out from the other items. The gap in understanding needs between \emph{finding defects} and \emph{code improvement} seems to corroborate our hypothesis that the difference in the number of comments about these two items in review comments is mostly due to understanding issues. Thus, if managers and developers want code review to match their need for \emph{finding defects}, context and change understanding must be improved.

@@

By observing developers performing code reviews, we noticed that some started code reviews by thoroughly reading the accompanying textual description, while others went directly to a specific changed file. In the first group, the time required for putting the first review comments and understanding the change rationale was noticeably longer, and some of the comments were asking to clarify the reasons for a change. To better comprehend this situation, we included in our interview guideline a question about how the interviewees start code reviews. Participants explained that when they own or are very familiar with the files being changed, they have a better context and it is easier for them to understand the change submitted: \quotation{when doing code review I start with things I am familiar with, so it is easier to see what is going on.} When they are file owners, they often do not need to read the description, but they \quotation{go directly to the files they own.} On the contrary, when they do not own files, or have to review new files, they need more information and try to get it from the description, which is deemed good when it states \quotation{what was changed and why.}

@@

Most of the respondents (798, \ie 91\%) answered positively to the first question, motivating it with the fact that it takes time to familiarize with the code and \quotation{learn enough about the files being modified to understand their purpose, invariants, APIs, etc.,} because \quotation{big-picture impact analysis requires contextual understanding. When reviewing a small, unfamiliar change, it is often necessary to read through much more code than that being reviewed.} The comment of a developer anticipates the answer to the second question: \quotation{It takes a lot longer to understand unknown code, but even then understanding isn't very deep. With code I am familiar with I have more to say. I know what to say faster. What I have to say is deeper. And I can be more insistent on it.} In fact, the answer to the second question is positive in 716~(82\%) cases. The main difference with file owner comments is that they are substantially deeper, more detailed and insightful. A respondent explained: \quotation{Comments reflect their deeper understanding -- more likely to find subtle defects, feedback is more conceptual (better ideas, approaches) instead of superficial (naming, mechanical style, etc.)} another tried to boldly summarize the concept: \quotation{Difference between algorithmic analysis and comments on coding style. The difference is big.}
In fact, when the context is clear and understanding is very high, as in the case when the reviewer is the owner of changed files, code review authors receive comments that explore \quotation{deeper details,} are \quotation{more directed} and \quotation{more actionable and pertinent,} and find \quotation{more subtle issues.}

### 2013-01-06 sections/conclusion.tex
put emphasis instead of quotes for categories

In this work, we have investigated modern, tool-based code review, uncovered both a wide range of motivations for review, and determined that the outcomes do not always match those motivations. We identified understanding as a key component and provided recommendations to both practitioners and researchers. It is our hope that the insights we have discovered lead to more effective review in practice and improved tools, based on research, to aid developers perform code reviews.

>>>>

In this work, we investigated modern, tool-based code review, uncovered both a wide range of motivations for review, and determined that the outcomes do not always match those motivations. We identified understanding as a key component and provided recommendations to both practitioners and researchers. It is our hope that the insights we have discovered lead to more effective review in practice and improved tools, based on research, to aid developers perform code reviews.

### 2013-01-06 sections/expectations.tex
put emphasis instead of quotes for categories

Almost all the managers included ``finding defects'' as one of the reasons for
doing code reviews; for 44\% of the managers, it is the top reason. Managers
considered defects to be both low level issues (\eg \quotation{correct logic
is in place}) and high level concerns (\eg \quotation{catch errors in
design}). Concerning surveyed developers/testers, ``finding defects'' is the
first motivation for code review for 383 of the programmers (44\%), second
motivation for 204 (23\%), and third for 96 (11\%).

@@

Nevertheless, even though ``finding defects'' emerged from our data as a strong
motivation (the first for almost half of the programmers and managers),
interviews and survey results indicate that this only tells part of the story
of why practitioners do code reviews and the outcomes they expect.

@@

Programmers ranked ``code improvement'' as an important motivation for code
review, close to ``finding defects:'' This is the primary motivation for 337
programmers (39\%), the second for 208 (24\%), and the third for 135 (15\%).
Managers reported code improvements as their primary motivation in 51 cases
(31\%). One manager wrote how code review in her view is a
\quotation{discipline of explaining your code to your peers {\normalfont[that]} drives a
higher standard of coding. I think the process is even more important than the
result.}

Most interviewed programmers mentioned that at least one of the reviewers
involved in each code review takes care of checking whether the code follows
the team conventions, for example in terms of code formatting and in terms of
function and variable naming. Some programmers use the ``code improvement''
check as a first step when doing code review: \quotation{the first basic pass
on the code is to check whether it is standard across the team.}

The interviews also gave us a glimpse of the connection between the quality of
code reviews and ``code improvement'' comments. Such comments seem easier to
write and sometimes interviewees mentioned them as the way reviewers use to
avoid spending time to conduct good code reviews. An observation by a senior
developer, in the company for more than nine years, summarizes the opinions we
received from many interviewees: \quotation{I've seen quite a few code reviews
where someone commented on formatting while missing the fact that there were
security issues or data model issues.}

@@

``Alternative solutions'' regard changes and comments on improving the
submitted code by adopting an idea that leads to a better implementation. This
is one of the few motivations in which developers and managers do not agree.
While 147~(17\%) developers put this as the first motivation, 202~(23\%) as the
second, and 152~(17\%) as the third, only 4~(2\%) managers even mentioned it
(\eg \quotation{Generate better ideas, alternative approaches} and
\quotation{Collective wisdom: Someone else on the project may have a better
idea to solve a problem}). The outcome of the interviews was similar to the
position of managers: Interviewees vaguely mentioned this motivation, and
mostly in terms of generic \quotation{better ways to do things.}

@@

All the interviewees but one motivated their code reviews also from a learning,
or ``knowledge transfer,'' perspective. With the words of a senior developer:
\quotation{one of the things that should be happening with code reviews over
time is a distribution of knowledge. If you do a code review and did not learn
anything about the area and you still do not know anything about the area, then
that was not as good code review as it could have been.} Although we did not
include questions related to ``knowledge transfer'' in our interview guideline,
this topic kept emerging spontaneously from each meeting, thus underscoring its
value for practitioners.

@@

Managers included ``knowledge transfer'' as one of the reasons for code review,
although never as the top motivation. They mostly wrote about code review as an
education means by mentioning among the motivations:
\quotation{developer education,} \quotation{education for junior developers who
are learning the codebase,} and \quotation{learning tool to teach more junior
team members.}

Programmers answering the survey declared ``knowledge transfer'' to be their
first motivation for code review in 73~(8\%) cases, their second in 119~(14\%),
and their third in 141~(16\%).

@@

The 873 programmers answering the survey ranked ``team awareness and
transparency'' very close to ``knowledge transfer.'' In fact, the two concepts
appeared logically related also in the interviews; for example one tester,
while reviewing some code said: \quotation{oh, this guy just implemented this
feature, and now let me back and use it somewhere else.} Showing that he both
learned about the new feature and he was now aware of the possibility to use it
in his own code. 75~(9\%) developers considered team awareness their first
motivation for code review, 108~(12\%) their second, and 149~(17\%) their
third.

Although team awareness and transparency emerged from our data as clearly
promoted by the code review process, academic research seems to have given
little attention to it.

@@

The concept of ``shared code ownership'' is closely related to ``team awareness
and transparency,'' but it has a stronger connotation toward active
collaboration and overlapping coding activities. Programmers and managers
believe that code review is not only an occasion to notify other team members
about incoming changes, but also a means to have more than one knowledgeable
person about specific parts of the codebase. A manager put the following as her
second motivation for code review: \quotation{Broaden knowledge \& understanding
of how specific features/areas are designed and implemented (e.g., grooming
``backup developers'' for areas where knowledge is too concentrated on one or
two expert developers).}

@@

In the programmers' survey, 51~(6\%) respondents marked ``share code
ownership'' as their first motivation, 100~(11\%) as their second, and 91~(10\%)
as their third.

@@

We discussed the five most prominent motivations, which show that ``finding
defects'' is the top motivation, although participants believe that code review
brings other benefits. The first two motivations were already popular in
research and their effectiveness have been evaluated in the context of code
inspections; on the contrary, the other motivations are still unexplored,
especially those regarding more ``social'' benefits on the team, such as shared
code ownership.

>>>>

Almost all the managers included \emph{finding defects} as one of the reasons for
doing code reviews; for 44\% of the managers, it is the top reason. Managers
considered defects to be both low level issues (\eg \quotation{correct logic
is in place}) and high level concerns (\eg \quotation{catch errors in
design}). Concerning surveyed developers/testers, \emph{finding defects} is the
first motivation for code review for 383 of the programmers (44\%), second
motivation for 204 (23\%), and third for 96 (11\%).

@@

Nevertheless, even though \emph{finding defects} emerged from our data as a strong
motivation (the first for almost half of the programmers and managers),
interviews and survey results indicate that this only tells part of the story
of why practitioners do code reviews and the outcomes they expect.

@@

Programmers ranked \emph{code improvement} as an important motivation for code
review, close to \emph{finding defects}: This is the primary motivation for 337~(39\%)
programmers, the second for 208~(24\%), and the third for 135~(15\%).
Managers reported \emph{code improvement} as their primary motivation in 51~(31\%) cases. One manager wrote how code review in her view is a
\quotation{discipline of explaining your code to your peers {\normalfont[that]} drives a
higher standard of coding. I think the process is even more important than the
result.}

Most interviewed programmers mentioned that at least one of the reviewers
involved in each code review takes care of checking whether the code follows
the team conventions, for example in terms of code formatting and in terms of
function and variable naming. Some programmers use a ``code improvement''
check as a first step when doing code review: \quotation{the first basic pass
on the code is to check whether it is standard across the team.}

The interviews also gave us a glimpse of the connection between the quality of
code reviews and code improvement comments. Such comments seem easier to
write and sometimes interviewees mentioned them as the way reviewers use to
avoid spending time to conduct good code reviews. An observation by a senior
developer, in the company for more than nine years, summarizes the opinions we
received from many interviewees: \quotation{I've seen quite a few code reviews
where someone commented on formatting while missing the fact that there were
security issues or data model issues.}

@@

\emph{Alternative solutions} regard changes and comments on improving the
submitted code by adopting an idea that leads to a better implementation. This
is one of the few motivations in which developers and managers do not agree.
While 147~(17\%) developers put this as the first motivation, 202~(23\%) as the
second, and 152~(17\%) as the third, only 4~(2\%) managers even mentioned it
(\eg \quotation{Generate better ideas, alternative approaches} and
\quotation{Collective wisdom: Someone else on the project may have a better
idea to solve a problem}). The outcome of the interviews was similar to the
position of managers: Interviewees vaguely mentioned this motivation, and
mostly in terms of generic \quotation{better ways to do things.}

@@

All the interviewees but one motivated their code reviews also from a learning---or \emph{knowledge transfer}---perspective. With the words of a senior developer:
\quotation{one of the things that should be happening with code reviews over
time is a distribution of knowledge. If you do a code review and did not learn
anything about the area and you still do not know anything about the area, then
that was not as good code review as it could have been.} Although we did not
include questions related to \emph{knowledge transfer} in our interview guideline,
this topic kept emerging spontaneously from each meeting, thus underscoring its
value for practitioners.

@@

Managers included \emph{knowledge transfer} as one of the reasons for code review,
although never as the top motivation. They mostly wrote about code review as an
education means by mentioning among the motivations:
\quotation{developer education,} \quotation{education for junior developers who
are learning the codebase,} and \quotation{learning tool to teach more junior
team members.}

Programmers answering the survey declared \emph{knowledge transfer} to be their
first motivation for code review in 73~(8\%) cases, their second in 119~(14\%),
and their third in 141~(16\%).

@@

The 873 programmers answering the survey ranked \emph{team awareness and
transparency} very close to \emph{knowledge transfer}. In fact, the two concepts
appeared logically related also in the interviews; for example one tester,
while reviewing some code said: \quotation{oh, this guy just implemented this
feature, and now let me back and use it somewhere else.} Showing that he both
learned about the new feature and he was now aware of the possibility to use it
in his own code. 75~(9\%) developers considered team awareness their first
motivation for code review, 108~(12\%) their second, and 149~(17\%) their
third.

Although \emph{team awareness and transparency} emerged from our data as clearly
promoted by the code review process, academic research seems to have given
little attention to it.

@@

The concept of \emph{shared code ownership} is closely related to \emph{team awareness
and transparency}, but it has a stronger connotation toward active
collaboration and overlapping coding activities. Programmers and managers
believe that code review is not only an occasion to notify other team members
about incoming changes, but also a means to have more than one knowledgeable
person about specific parts of the codebase. A manager put the following as her
second motivation for code review: \quotation{Broaden knowledge \& understanding
of how specific features/areas are designed and implemented (e.g., grooming
``backup developers'' for areas where knowledge is too concentrated on one or
two expert developers).}

@@

In the programmers' survey, 51~(6\%) respondents marked \emph{share code
ownership} as their first motivation, 100~(11\%) as their second, and 91~(10\%)
as their third.

@@

We discussed the five most prominent motivations, which show that \emph{finding
defects} is the top motivation, although participants believe that code review
brings other benefits. The first two motivations were already popular in
research and their effectiveness have been evaluated in the context of code
inspections; on the contrary, the other motivations are still unexplored,
especially those regarding more social benefits on the team, such as shared
code ownership.

### 2013-01-06 sections/implications.tex
put emphasis instead of quotes for categories

\textbf{Automate Code Review Tasks:} We observed that many code review comments were related to ``code improvement'' concerns and low-level ``micro'' defects. Identifying both of these are problems that research has begun to solve. Tools for enforcing team code conventions, checking for typos, and identifying dead code already exist. Even more advanced tasks such as checking boundary conditions or catching common mistakes have been shown to work in practice on real code. For example Google experimented with adding FindBugs to their review process, though little is reported about the results~\cite{ayewah2007using}. Automating these tasks frees reviewers to look for deeper, more subtle defects. Code review is fertile ground to have an impact with code analysis tools.

>>>>

\textbf{Automate Code Review Tasks:} We observed that many code review comments were related to \emph{code improvement} concerns and low-level ``micro'' defects. Identifying both of these are problems that research has begun to solve. Tools for enforcing team code conventions, checking for typos, and identifying dead code already exist. Even more advanced tasks such as checking boundary conditions or catching common mistakes have been shown to work in practice on real code. For example Google experimented with adding FindBugs to their review process, though little is reported about the results~\cite{ayewah2007using}. Automating these tasks frees reviewers to look for deeper, more subtle defects. Code review is fertile ground to have an impact with code analysis tools.

### 2013-01-06 sections/limitations.tex
put emphasis instead of quotes for categories

Based on review comments, survey responses, and interviews, we know that in-person discussions occurred frequently. While we are unable to compare frequency of these events to other outcomes as we can with events that are recorded in CodeFlow, we know that they most often occurred to address understanding needs.

>>>>

Based on review comments, survey responses, and interviews, we know that in-person discussions occurred frequently. While we cannot compare frequency of these events to other outcomes as we can with events recorded in CodeFlow, we know that they most often occurred to address understanding needs.

### 2013-01-06 sections/methodology.tex
put emphasis instead of quotes for categories

\textbf{5. Affinity Diagram:} We used an \emph{affinity diagram} to organize the categories
that emerged from the card sort. This tool allows large numbers of ideas to be
sorted into groups for review and analysis~\cite{shade2000improving}. We used it
to generate an overview of the topics that emerged from the card sort, in order
to connect the related concepts and derive the main themes. For generating the
affinity diagram, we followed the five canonical steps: we \begin{inparaenum}[(1)] 
\item recorded the categories on post-it-notes, 
\item spread them onto a wall, 
\item sorted the categories based on discussions, until all are sorted and all participants agreed, 
\item named each group with a description, and 
\item captured and discussed the themes.
\end{inparaenum}

@@

We sent the first survey to a cross section of managers.  We considered
managers for which at least half of their team performed code reviews regularly
(on average, one per week or more) and sampled along two dimensions.  The first
dimension was whether or not the manager had participated in a code review
himself since the beginning of the year and the second dimension was whether
the manager managed a single team or multiple teams (a manager of managers).
Thus, we had one sample of first level managers who participated in review,
another sample of second level managers who participated in reviews, \etc  The
first survey was a short survey comprising 6 questions (all optional), which we
sent to 600 managers that had at least ten direct or indirect reporting
developers who used CodeFlow in the past. The central focus was the open
question asking to enumerate the main motivations for doing code reviews in
their team. We received 165 answers (28\% response rate), which we analyzed
before devising the second survey.

>>>>

\textbf{5. Affinity Diagram:} We used an \emph{affinity diagram} to organize the categories
that emerged from the card sort. This tool allows large numbers of ideas to be
sorted into groups for review and analysis~\cite{shade2000improving}. We used it
to generate an overview of the topics that emerged from the card sort, in order
to connect the related concepts and derive the main themes. For generating the
affinity diagram, we followed the five canonical steps: we \begin{inparaenum}[(1)] 
\item recorded the categories on post-it-notes, 
\item spread them onto a wall, 
\item sorted the categories based on discussions, until all are sorted and all participants agreed, 
\item named each group, and 
\item captured and discussed the themes.
\end{inparaenum}

@@

We sent the first survey to a cross section of managers.  We considered
managers for which at least half of their team performed code reviews regularly
(on average, one per week or more) and sampled along two dimensions.  The first
dimension was whether or not the manager had participated in a code review
himself since the beginning of the year and the second dimension was whether
the manager managed a single team or multiple teams (a manager of managers).
Thus, we had one sample of first level managers who participated in review,
another sample of second level managers who participated in reviews, \etc  The
first survey was a short survey comprising 6 questions (all optional), which we
sent to 600 managers that had at least 10 direct or indirect reporting
developers who used CodeFlow. The central focus was the open
question asking to enumerate the main motivations for doing code reviews in
their team. We received 165 answers (28\% response rate), which we analyzed
before devising the second survey.

### 2013-01-06 sections/outcomes.tex
put emphasis instead of quotes for categories

%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion} \label{sec:conclusion}
%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%
\section{The Outcomes of Code Reviews} \label{sec:outcomes}
%%%%%%%%%%%%%%%%%%%%%%

Our second research question seeks to understand what the actual outcomes of code reviews are, and whether they match the motivations and expectations outlined in the previous section. To that end, we conducted indirect field research~\cite{lethbridge2005studying} by analyzing the content of 200 threads (corresponding to 570 comments) recorded by CodeFlow. \figref{XXX4} shows the categories of comments found through the card sort.

\textbf{Code Improvements:} The most frequent category, with 165~(29\%) comments, is \emph{code improvements}. In detail, among \emph{code improvements} comments we find 58 on using better code practices, 55 on removing not necessary or unused code, and 52 on improving code readability.

\textbf{Defect Finding:} Although \emph{defect finding} is the top motivation and expected outcome of code review for many practitioners, the category \emph{defect} is the only the fourth most frequent, out of nine items, with 78 (14\%) comments. Among \emph{defect} comments, 65 are on logical issues (\eg a wrong expression in an if clause), 6 on high-level issues, 5 on security, and 3 on wrong exception handling.

\textbf{Knowledge Transfer:} Concerning the other expected outcomes of code reviews, we did not expect to find evidence about them, because of their more ``social''--thus harder to quantify—nature. Nevertheless, we found some (12) comments specifically about \emph{knowledge transfer}, where the reviewers were directing the code change author to external resources (\eg internal documentation or websites) for learning how to tackle some issues. This provides additional evidence on the importance of this aspect of reviews.

\subsection{Finding defects: When expectations do not meet reality}

Why do we see this significant gap in frequency between \emph{code improvements} and \emph{defects} comments? Possible reasons may be that our sample of 570 comments is too small to represent the population, that the submitted changes might require less need fixing of ``real'' defects than of small code improvements, or that programmers could consider \emph{code improvements} as actual defects. However, by triangulating these numbers with the interview discussions, the survey answers, and the other categories of comments, another reason seems to justify this situation. First, we start by noting that most of the comments on \emph{defects} regard uncomplicated logical errors, \eg corner cases, common configuration values, or operator precedence. Then, from interview data, we see that: \begin{inparaenum}[(1)]
\item most interviewees explained how, with tool-based code reviews, most of the found defects regard \quotation{logic issues--where the author might not have considered a particular or corner case}; 
\item some interviewees complained that the quality of code reviews is low, because reviewers only look for easy errors: \quotation{{\normalfont [Some reviewers]} focus on formatting mistakes because they are easy {\normalfont [...]}, but it doesn't really help. {\normalfont [...]} In some ways it's kind of embarrassing if someone asks you to do a code review and all you can find are formatting mistakes when there are real mistakes to be found}; and 
\item other interviewees admitted that if the code is not among their codebase, they look at \quotation{obvious bugs (such as, exception handling).} Finally, managers mentioned \quotation{catching early obvious bugs} or \quotation{finding obvious inefficiencies or errors} as reasons for doing code review.
\end{inparaenum}
These points illustrate that the reason for the gap between the number of comments on \emph{code improvements} and on \emph{defects} is not to be found in problems in the sample or in classification misconceptions, but it is rather just additional corroborating evidence that the outcome of code review does not match the main expectation of both programmers and managers—finding defects. Review comments about defects are few, comprising one-eighth of the total in our sample, and mostly address ``micro'' level and superficial concerns; while programmers and managers would expect more insightful remarks on conceptual and design level issues. Why does this happen? The high frequency of understanding comments hints at the answer to our question, addressed in the next section.
